Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
sup

\noindent\textbf{I. Detailed Interpretation of Experimental Results}

\ul{(1) Table.~1: ``Mean \& Variance ...'''}

\ul{(2) Table.~2: ``... Source \& Destination Hardness ...''}

\ul{(3) Table.~3: ``Hardness Manipulation ...'' and Fig.~6}

\ul{(4) Table.~4: ``... Graduate Adversary ...'' and Fig.~7}

\ul{(5) Table.~5: ``Intra-Class Structure ...'' and Fig.~8}

\ul{(6) Table.~6: ``... State-of-The-Art ...''}

\oo{todo}

@@

In the manuscript, the training cost of adversarial training is caluclated as
$\eta+1$, which is a theoretical number of forward-backward propagation
involved in each iteration of the training process.
%
The wall time is not used, because the wall time is noisy, and will be affected
by many irrevevant factors which eventually makes the result uncomparable or
unfair.
%
The factors that affect the wall time for adversarial training include but are
not limited to:
%
(1) GPU Performance. For instance, the wall time reported based on eight Nvidia
A100 GPUs will not be valuable for readers who do not have access to the same
hardware;
%
(2) System load when training, CPU performance, and I/O device performance;
%
(3) Code implementation and engineering tricks. Well-optimized code will
consume less time.
%
Namely, the wall time is a noisy measure of training cost which will render
invalid comparison or unfair comparison.
%
In contrast, the training cost measure ($\eta+1$) in the manuscript has
isolated all irrelevant factors.

For reference, the most time-consuming experiment is
HM[$\mathcal{S},g_\mathsf{LGA}$] on the SOP dataset.
%
When $\eta=8$, the experiment takes $32$ hours with two Nvidia Titan Xp GPUs;
%
When $\eta=32$, the experiment takes $105$ hours with two Nvidia Titan Xp GPUs.

>>>>

@@

In the manuscript, the training cost of adversarial training is caluclated as
$\eta+1$, which is the number of forward-backward propagation involved in each
iteration of the training process, in order to reflect the training efficiency
(gain as high robustness as possible given a fixed number of foward-backward
calculation for adversarial training) of different defense methods.
%
Specifically, PGD creates adversarial examples from the $\eta$ times of
forward-backward computation.
%
With the resulting adversarial examples, the network requires once
more forward-backward computation to update the model parameters.
